Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-03-01 paper/main.tex

\subsection*{additional contrasts}

\todo[inline]{remove subheadings}

\todo[inline]{introductory \& concluding sentences}

\subsubsection*{PPA, RSC, and LOC (AV \& AV)}

\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}

\todo[inline]{I manually adjusted the stability-slices.pdf; the Fig S1 should
now (not just on my computer) show a black bar in the color maps for the
audio-descriptions (because there are 5 and not 8 contrasts)}

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
audio-description (see Table~\ref{tab:contrasts}).
% how
Contrasts differ in contrasted categories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

% intro
For each naturalistic stimulus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for XYZ\todo{yes, to test what?} within the movie fMRI data, we created
four contrasts that compared hemodynamic activity during frames within movie
shots (\texttt{no\_cut} category) with movie cut related categories
(see Table~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster.
%
Null results of control contrasts comparing frames within movie shots to frames
immediately after a cut suggest that XYZ.
%
\todo[inline]{concluding statement}

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
The inspection of correlations of regressors across stimuli
(see Figure~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
depicted for the first time (\texttt{vse\_new}) and nouns indicating a switch to
a setting occurring for the first time (\texttt{se\_new}), and cuts to a
recurringly depicted setting ({\texttt{vse\_old}) and nouns indicating a switch
a recurring setting (\texttt{se\_old}.
%
Hence, we created a contrast that used the audio-description's nouns on the
movie data ({\texttt{se\_new} > \texttt{se\_old}).
% results
The contrasts yielded a significant cluster in the right [but not anterior] PPA
and bilateral clusters in the superior lateral occipital cortices (the right
hemispheric cluster extending into the superior parietal cortex).
%
Results suggest that XYZ.
%
\todo[inline]{concluding statement? That last contrast was originally done to
check that "soundscape at moment of cuts thing" but this is obsolete now}

\todo{following: control contrast for AO; why exactly did we do this except "we
do not expect (lots of) significant cluster because negative control?}

% AD stimulus
Finally for the analysis of the audio-description, we created control contrasts
based on events of the annotated movie cuts (see Table~\ref{tab:contrasts}) in
order to test XYZ.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.  \todo{not PPA! explanation?}
%
Overall results from the negative control contrast of the audio-description's
data suggest that XYZ.
%
\todo[inline]{concluding statement?}

>>>>

\subsection*{Robustness of main findings across alternative contrasts}

In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus, and overall eight $t$-contrast for the
audio-description (see Table~\ref{tab:contrasts}).
% how
Contrasts differ in contrasted categories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

% intro
For each naturalistic stimulus, we created several control contrasts.
% movie contrasts: not cut condition vs. cuts
To test for the specificity of the main finds within the movie fMRI data, we created
four contrasts that compared hemodynamic activity during frames within movie
shots (\texttt{no\_cut} category) with movie cut related categories
(see Table~\ref{tab:contrasts}).
% results
None of these four contrasts yielded a significant cluster, suggesting that
the observed differential hemodynamic response in the PPA for events defined
by particular movie cuts is not observed for other arbitrarily selected time point
in the movie.

% \texttt{se\_new} (nouns) is r$\approx$0.3 correlated with \texttt{vse\_new}
% (cuts); \texttt{se\_old} (nouns) is r$\approx$0.4 correlated with
% \texttt{vse\_old}.
The correlation of regressors across stimuli
(Figure~\ref{fig:reg-corr}) showed a moderate correlation among cuts to a setting
depicted for the first time (movie \texttt{vse\_new}) and nouns indicating a switch to
a setting occurring for the first time (audio-description \texttt{se\_new}), and cuts to a
recurringly depicted setting (movie {\texttt{vse\_old}) and nouns indicating a switch
a recurring setting (audio-description \texttt{se\_old}).
%
Hence, we computed an indentical contrast ({\texttt{se\_new} >
\texttt{se\_old}), comparing the audio-description's voice-over narrator
nouns for the movie data and the audio-description.
% results
While for the movie data the contrast yielded a significant cluster in the
right PPA, not in its anterior portion, and bilateral clusters in the
superior lateral occipital cortices (the right hemispheric cluster extending
into the superior parietal cortex), not significant differences where found
for the audio-description (unthresholded contrast maps are available on NeuroVault).
%
These results suggest that in the absence of the actual visual stimulation, the narrator's
description of scene properties correlated with setting changes did not co-occur with
increased hemodynamic activity in areas associated with the processing of spatial
information.

% AD stimulus
Finally for the analysis of the audio-description, we computed control contrasts
based on events of the annotated movie cuts (Table~\ref{tab:contrasts}) in
order to evaluate the influence of stimulus features correlated with these visual
events that remain present in the audio-description, such as changes in the soundscape.
% results
Two of five contrasts yielded significant clusters.
% contrast 9
Contrast 9 (\texttt{vse\_new > pe\_old}) revealed one significant cluster in the
left inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus.
%
The absence of observable hemodynamic response differences in the PPA suggests that
without the visual information in the movie stimulus, no, or substantially less,
processing of stimulus content with respect to spatial information co-occurred with
the timing of the movie cuts.
